Aa Language Reference Manual

### 2018-11-25 v2/Ahir-asm/devel/docs/AaLRM.tex
Uncovered a beauty of a bug due to rollover of time stamps in the memory subsystem.  For now, increase the time stamp range to reduce the likelihood of any screw ups.  Keep it at least 10 for now..

{\bf Aa} is a programming language for the 
description of algorithms.   The control-flow
in an \Aa program corresponds to a petri net
of a specific class.
The data-flow is constructed using static
single-assignment variables (which can be assigned to only once),
storage objects, messaging pipes and constants.
Pointers to storage objects can be created
and manipulated (pointer arithmetic, dereferencing
etc.) in the usual way.

@@

\subsection{Operator Modules}

@@

\subsection{Volatile Modules}

>>>>

{\bf Aa} is a programming language for the 
description of algorithms, with the ultimate aim
being the conversion of these algorithms into 
a hardware implementation.   The control-flow
in an \Aa program corresponds to a petri net
of a specific class.
The data-flow is constructed using static
single-assignment variables (which can be assigned to only once),
storage objects, messaging pipes and constants.
Pointers to storage objects can be created
and manipulated (pointer arithmetic, dereferencing
etc.) in the usual way.

@@

\subsection{Deterministic Pipelined Modules}

In certain situations, we are sure that all operations inside
a module are deterministic, that is, we know that they take
a fixed amount of time.  Examples of such operations are 
addition, subtraction etc. which are mapped to unshared
operators.  Examples of operations which are not deterministic
are pipe accesses and accesses to shared memory.

If we are sure that all operations are deterministic, then
we can add a qualifier to the pipelined module.  For instance
\begin{verbatim}
$pipeline $depth 3 $deterministic $operator
        $module [foo] $in (A B: $uint<8>) $out (C: $uint<8>) $is
{
   U := A
   V := (U + B)
   W := (V + A)
   C  := (W + B)
}
\end{verbatim}
This module will then eventually be implemented in VHDL
using much simpler control logic.

Pipelined modules have the following restrictions:
\begin{itemize}
\item Their internal structure is that of an
operator module (Section \ref{sec:OperatorModules}).
\item They can not access memory.
\item They can not access pipes.
\item The only write-after-read sequences permitted
are of an accumulation type, for example
\begin{verbatim}
a := (a + 1)
\end{verbatim}
\item They can call other modules only if the called
modules are either volatile (Section \ref{sec:VolatileModules}) or deterministic pipelines.
\end{itemize}

In many cases, the core computation is completely
deterministic, and we can save considerable hardware
by collecting it into a deterministic pipeline.

\subsection{Operator Modules} \label{sec:OperatorModules}

@@

\subsection{Volatile Modules} \label{sec:VolatileModules}
